---
title: "Project: Lever-Up"
author: "Art Tay"
date: "12/25/2020"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
fig_width: 6
fig_height: 6
---

# Theory

Theory: A portfolio that invests in the S&P 500 and Long-Term US treasuries is a good investment, and leverage turns good investments into great investments. Therefore, investing in a leveraged ETFs that track these two indices is a great investment. 

# Methodolgy

Testing Period: 2010-1-1 to 2020-12-23

Testing Metrics: Quarterly Returns, Standard Deviation, Efficicency Frontiers, Cummulative Return, Sharpe Ratio

Testing Units: 
1. SPXL: Direxion Daily S&P 500 Bull 3x 
2. TMF: Direxion Daily 20-Year Treasury Bull 3x
3. SPY: S&P 500 ETF 
4. VGLT: Vanguard Long-Term Treasury 

```{r, include = F}
#imports
library(quantmod)
library(tidyverse)
library(car)
library(corrplot)
library(knitr)
library(gtsummary)

#Date Setup 

start = as.Date("2010-1-1")
end = as.Date("2020-12-23")
```

# Background 
```{r, echo = F, message = F}
#data pull 
tickers = c("SPY", "SPXL", "VGLT", "TMF")

background = data.frame()

for(tick in tickers){
  background = cbind(background, annualReturn(getSymbols(Symbols = tick, auto.assign = F, from = start, to = end)))
}

colnames(background) = tickers 

#Return Plots 
background_long = cbind(index(background), as.data.frame(background)) %>% gather(key = "Ticker", value = "Annual Returns", 2:5)
background_returns = ggplot(data = background_long, aes(x = `index(background)`, y = `Annual Returns`, 
                                                        col = Ticker)) + labs(x = "Time")

background_returns + geom_line() + ggtitle("Fig. 1: Annual Return Comparison Plot") 

#Boxplot 
background_returns + geom_boxplot() + ggtitle("Fig. 2: Annual Return Variability") 

#Cummlative Plot 
background_cum = apply(background, 2, FUN = function(x){
  cumprod(x + 1) 
})
background_cum = cbind(index(background), as.data.frame(background_cum)) %>% gather(key = "Ticker", value = "Cummulative Returns", 2:5)

background_cum_plot = ggplot(data = background_cum, aes(x = `index(background)`, y = `Cummulative Returns`, col = Ticker))

background_cum_plot + labs(x = "Time", y = "$") + geom_line() + ggtitle("Fig. 3: Value of $1 Investment")

```

```{r, echo = F}
#Correlation Plot 
corrplot(cor(background), method= "number", title = "Fig. 5: Correlation Plot", mar  = c(0,0,1,0))

#Sharpe Ratios 
means = apply(background, 2, FUN = mean)
SDs = apply(background, 2, sd)
sharpes = means / SDs

sumStats = rbind(means, SDs, sharpes)
kable(x = sumStats, caption = "Fig. 6: Summary Statistics")

```


# S&P 500

1. How close are the daily adjusted returns to 3x? 
```{r, echo = F}
#Get SPY data
SPY = getSymbols(Symbol = "SPY", auto.assign = F, from = start, to = end)

#Calc Daily Returns 
SPY_daily = dailyReturn(SPY)


#Get SPXL data
SPXL = getSymbols(Symbol = "SPXL", auto.assign = F, from = start, to = end)

#Calc Daily Returns 
SPXL_daily = dailyReturn(SPXL)


#Scatterplot 
Daily_Returns = cbind(SPY_daily, SPXL_daily)
colnames(Daily_Returns) = c("SPY", "SPXL")
Daily_Returns_Plot = ggplot(data = Daily_Returns, aes(SPY, SPXL))+geom_point()

#Regression
mod1 = lm(data = Daily_Returns, formula = SPXL ~ SPY)
b1 = mod1$coefficients[1]
b2 = mod1$coefficients[2]

#Plot
Daily_Returns_Plot + geom_abline(intercept = b1, slope = b2, col = "red") + ggtitle("Fig. 7: Comparison of Daily Returns")
(smod1 = summary(mod1))

```

$$
\begin{align} 
H_0:\beta_2=3\\
H_a:\beta_2\neq3\\
t=\dfrac{\hat{\beta_2}-H_0}{SE(\hat{\beta_2})}
\end{align}
$$


```{r, include = F}
#t-test
SE_b2 = smod1$coefficients[2,2]
t = (b2 - 3)/SE_b2 
df = smod1$df[2]
p_value = 2 * pt(abs(t), df, lower.tail = F)

p_intercept = smod1$coefficients[1,4]
```

According to the regression the intercept term is not significant (p=`r p_intercept`). Furthermore according to a t-test on $\beta_2$ the is not sufficient evidence to say that the coefficient differs from 3 at $\alpha = 1\%$(p=`r p_value`). It is worth noting that the p-value is significant at 5%. This means that SPXL give very close to 3x exposure, but most likely due to fees it is a little bit less (say 2.99x).  

2. What is the relationship between their cummulative annual returns? 
Note: 2020 is not a full year at the time of formulation 
```{r, echo = F}
#calc annual returns for SPY
SPY_annual = annualReturn(SPY)

#calc cummulative returns 
SPY_annual$Cumulative = cumprod(SPY_annual$yearly.returns + 1) - 1

#calc annual returns for SPXL
SPXL_annual = annualReturn(SPXL)
#calc cummulative returns 
SPXL_annual$Cumulative = cumprod(SPXL_annual$yearly.returns + 1) - 1

#scatterplot
Annual_Returns = cbind(SPY_annual$Cumulative, SPXL_annual$Cumulative)
colnames(Annual_Returns) = c("SPY", "SPXL")
Annual_Returns_Plot = ggplot(data = Annual_Returns, aes(SPY, SPXL))+geom_point()

# #Full Model
# mod2 = lm(data = Annual_Returns, formula = SPXL ~ SPY + I(SPY^2))
# (smod2 = summary(mod2))
# paste("AIC =", AIC(mod2))
# paste("BIC =", BIC(mod2))

#Linear Only
mod3 = lm(data = Annual_Returns, formula = SPXL ~ SPY)

#paste("AIC =", AIC(mod3))
#paste("BIC =", BIC(mod3))

b1_2 = mod3$coefficients[1]
b2_2 = mod3$coefficients[2]

Annual_Returns_Plot + geom_abline(intercept = b1_2, slope = b2_2, col = "red") + ggtitle("Fig. 8: Comparison of Annual Cumulative Returns")
(smod3 = summary(mod3))

# 
# #Quadratic Only
# mod4 = lm(data = Annual_Returns, formula = SPXL ~ I(SPY^2))
# (smod4 = summary(mod4))
# paste("AIC =", AIC(mod3))
# paste("BIC =", BIC(mod3))

```
The relationship between the two ETFs's annual cumulative returns appears to be linear. Both coefficients are significant.  

```{r, echo = F}
#weekly 
annual_Returns = cbind(annualReturn(SPY), annualReturn(SPXL)) 
colnames(annual_Returns) = c("SPY", "SPXL")

#scatterplot 
annual_Returns_Plot = ggplot(data = annual_Returns, aes(SPY, SPXL)) + geom_point()

#regression 
annualmod = lm(data = annual_Returns, formula = SPXL ~ SPY)


b1_annual = annualmod$coefficients[1]
b2_annual = annualmod$coefficients[2]

annual_Returns_Plot + geom_abline(intercept = b1_annual, slope = b2_annual, col = "red") + ggtitle("Fig. 9: Comparison of Annual Returns")
(sannualmod = summary(annualmod))
```



# Long Term US Treasuries
1. How close are the daily returns to 3x? 
```{r, echo = F}
#Get SPY data
VGLT = getSymbols(Symbol = "VGLT", auto.assign = F, from = start, to = end)

#Calc Daily Returns 
VGLT_daily = dailyReturn(VGLT)


#Get SPXL data
TMF = getSymbols(Symbol = "TMF", auto.assign = F, from = start, to = end)

#Calc Daily Returns 
TMF_daily = dailyReturn(TMF)


#Scatterplot 
Daily_Returns_Bonds = cbind(VGLT_daily, TMF_daily)
colnames(Daily_Returns_Bonds) = c("VGLT", "TMF")
Daily_Returns_Plot_Bonds = ggplot(data = Daily_Returns_Bonds, aes(VGLT, TMF))+geom_point()

#Regression
mod4 = lm(data = Daily_Returns_Bonds, formula = TMF ~ VGLT)

b1 = mod4$coefficients[1]
b2 = mod4$coefficients[2]

#Plot
Daily_Returns_Plot_Bonds + geom_abline(intercept = b1, slope = b2, col = "red") + ggtitle("Fig. 10: Comparison of Daily Returns")
(smod4 = summary(mod4))
```

```{r, echo = F}
SE_b2 = smod4$coefficients[2,2]
t = (b2 - 3)/SE_b2 
df = smod4$df[2]
p_value = 2 * pt(abs(t), df, lower.tail = F)

p_intercept = smod4$coefficients[1,4]
```

Although the intercept term is not significant(p = `r p_intercept`), we are fairly confident that the true value for $\beta_2$ differs from 3 (p=`r p_value`). The true leverage value is most likely greater than 3 (t = `r t`).  

2. What is the relation between the annual returns? 
```{r, echo = F}
#annual return comparison
bond_annual = cbind(annualReturn(VGLT), annualReturn(TMF))
colnames(bond_annual) = c("VGLT", "TMF")

bond_annual_plot = ggplot(data = bond_annual, aes(x = VGLT, y = TMF)) + geom_point()

mod5 = lm(data = bond_annual, formula = TMF ~ VGLT)
b1 = mod5$coefficients[1]
b2 = mod5$coefficients[2]

bond_annual_plot + ggtitle("Fig. 11: Annual Return Comparison") + geom_abline(intercept = b1, slope = b2, col = "red")  
(smod5 = summary(mod5))

#cummulative return comparison 
bond_cum = as.data.frame(apply(bond_annual, 2, FUN = function(x){cumprod(x+1)-1}))

bond_cum_plot = ggplot(data = bond_cum, aes(x = VGLT, y = TMF)) + geom_point()

mod6 = lm(data = bond_cum, formula = TMF ~ VGLT)

b1 = mod6$coefficients[1]
b2 = mod6$coefficients[2]

bond_cum_plot + ggtitle("Fig. 12: Cumulative Annual Return Comparison") + geom_abline(intercept = b1, slope = b2, col = "red")
(smod6 = summary(mod6))

```


# Portfolio Testings 
```{r, echo = F}
#10 years 
weights = seq(from = 0, to = 1, by = .01)
weights = cbind(weights, 1 - weights)

#SPY_VGLT
SPY_VGLT = cbind(annualReturn(SPY), annualReturn(VGLT))
port_1 = SPY_VGLT %*% t(weights)
port_1_plot = cbind(apply(port_1, 2, FUN = mean), apply(port_1, 2, FUN = sd), weights)
port_1_plot = as.data.frame(port_1_plot)
port_1_plot$sharpe = port_1_plot$V1/port_1_plot$V2
port_1_plot$Label = "SPY_VGLT"
colnames(port_1_plot) = c("E[R]", "Sigma", "W1", "W2", "Sharpe", "Asset Mix")

#SPXL_TMF
SPXL_TMF = cbind(annualReturn(SPXL), annualReturn(TMF))
port_2 = SPXL_TMF %*% t(weights)
port_2_plot = cbind(apply(port_2, 2, FUN = mean), apply(port_2, 2, FUN = sd), weights)
port_2_plot = as.data.frame(port_2_plot)
port_2_plot$sharpe = port_2_plot$V1/port_2_plot$V2
port_2_plot$Label = "SPXL_TMF"
colnames(port_2_plot) = c("E[R]", "Sigma", "W1", "W2", "Sharpe", "Asset Mix")

#SPY_TMF
SPY_TMF = cbind(annualReturn(SPY), annualReturn(TMF))
port_3 = SPY_TMF %*% t(weights)
port_3_plot = cbind(apply(port_3, 2, FUN = mean), apply(port_3, 2, FUN = sd), weights)
port_3_plot = as.data.frame(port_3_plot)
port_3_plot$sharpe = port_3_plot$V1/port_3_plot$V2
port_3_plot$Label = "SPY_TMF"
colnames(port_3_plot) = c("E[R]", "Sigma", "W1", "W2", "Sharpe", "Asset Mix")

#SPXL_VGLT
SPXL_VGLT = cbind(annualReturn(SPXL), annualReturn(VGLT))
port_4 = SPXL_VGLT %*% t(weights)
port_4_plot = cbind(apply(port_4, 2, FUN = mean), apply(port_4, 2, FUN = sd), weights)
port_4_plot = as.data.frame(port_4_plot)
port_4_plot$sharpe = port_4_plot$V1/port_4_plot$V2
port_4_plot$Label = "SPXL_VGLT"
colnames(port_4_plot) = c("E[R]", "Sigma", "W1", "W2", "Sharpe", "Asset Mix")

EF = rbind(port_1_plot, port_2_plot, port_3_plot, port_4_plot)

EF_plot = ggplot(data = EF, aes(x = Sigma, y = `E[R]`, col = `Asset Mix`)) + geom_point()
EF_plot = EF_plot + ggtitle("Fig. 13: Last 10 Years Efficiency Frontiers") 
EF_plot + geom_abline(slope = max(EF$Sharpe))

kable(EF %>% group_by(`Asset Mix`) %>% filter(`Sharpe` == max(`Sharpe`))) 

```

```{r, echo = F}
#5 Year

SPY = SPY["2015/"]
SPXL = SPXL["2015/"]
VGLT = VGLT["2015/"]
TMF = TMF["2015/"]

#SPY_VGLT
SPY_VGLT = cbind(annualReturn(SPY), annualReturn(VGLT))
port_1 = SPY_VGLT %*% t(weights)
port_1_plot = cbind(apply(port_1, 2, FUN = mean), apply(port_1, 2, FUN = sd), weights)
port_1_plot = as.data.frame(port_1_plot)
port_1_plot$sharpe = port_1_plot$V1/port_1_plot$V2
port_1_plot$Label = "SPY_VGLT"
colnames(port_1_plot) = c("E[R]", "Sigma", "W1", "W2", "Sharpe", "Asset Mix")

#SPXL_TMF
SPXL_TMF = cbind(annualReturn(SPXL), annualReturn(TMF))
port_2 = SPXL_TMF %*% t(weights)
port_2_plot = cbind(apply(port_2, 2, FUN = mean), apply(port_2, 2, FUN = sd), weights)
port_2_plot = as.data.frame(port_2_plot)
port_2_plot$sharpe = port_2_plot$V1/port_2_plot$V2
port_2_plot$Label = "SPXL_TMF"
colnames(port_2_plot) = c("E[R]", "Sigma", "W1", "W2", "Sharpe", "Asset Mix")

#SPY_TMF
SPY_TMF = cbind(annualReturn(SPY), annualReturn(TMF))
port_3 = SPY_TMF %*% t(weights)
port_3_plot = cbind(apply(port_3, 2, FUN = mean), apply(port_3, 2, FUN = sd), weights)
port_3_plot = as.data.frame(port_3_plot)
port_3_plot$sharpe = port_3_plot$V1/port_3_plot$V2
port_3_plot$Label = "SPY_TMF"
colnames(port_3_plot) = c("E[R]", "Sigma", "W1", "W2", "Sharpe", "Asset Mix")

#SPXL_VGLT
SPXL_VGLT = cbind(annualReturn(SPXL), annualReturn(VGLT))
port_4 = SPXL_VGLT %*% t(weights)
port_4_plot = cbind(apply(port_4, 2, FUN = mean), apply(port_4, 2, FUN = sd), weights)
port_4_plot = as.data.frame(port_4_plot)
port_4_plot$sharpe = port_4_plot$V1/port_4_plot$V2
port_4_plot$Label = "SPXL_VGLT"
colnames(port_4_plot) = c("E[R]", "Sigma", "W1", "W2", "Sharpe", "Asset Mix")

EF = rbind(port_1_plot, port_2_plot, port_3_plot, port_4_plot)

EF_plot = ggplot(data = EF, aes(x = Sigma, y = `E[R]`, col = `Asset Mix`)) + geom_point()
EF_plot = EF_plot + ggtitle("Fig. 14: Last 5 Years Efficiency Frontiers") 
EF_plot + geom_abline(slope = max(EF$Sharpe))

kable(EF %>% group_by(`Asset Mix`) %>% filter(`Sharpe` == max(`Sharpe`)))
```

```{r, echo = F}
SPY = SPY["2017/"]
SPXL = SPXL["2017/"]
VGLT = VGLT["2017/"]
TMF = TMF["2017/"]

#SPY_VGLT
SPY_VGLT = cbind(annualReturn(SPY), annualReturn(VGLT))
port_1 = SPY_VGLT %*% t(weights)
port_1_plot = cbind(apply(port_1, 2, FUN = mean), apply(port_1, 2, FUN = sd), weights)
port_1_plot = as.data.frame(port_1_plot)
port_1_plot$sharpe = port_1_plot$V1/port_1_plot$V2
port_1_plot$Label = "SPY_VGLT"
colnames(port_1_plot) = c("E[R]", "Sigma", "W1", "W2", "Sharpe", "Asset Mix")

#SPXL_TMF
SPXL_TMF = cbind(annualReturn(SPXL), annualReturn(TMF))
port_2 = SPXL_TMF %*% t(weights)
port_2_plot = cbind(apply(port_2, 2, FUN = mean), apply(port_2, 2, FUN = sd), weights)
port_2_plot = as.data.frame(port_2_plot)
port_2_plot$sharpe = port_2_plot$V1/port_2_plot$V2
port_2_plot$Label = "SPXL_TMF"
colnames(port_2_plot) = c("E[R]", "Sigma", "W1", "W2", "Sharpe", "Asset Mix")

#SPY_TMF
SPY_TMF = cbind(annualReturn(SPY), annualReturn(TMF))
port_3 = SPY_TMF %*% t(weights)
port_3_plot = cbind(apply(port_3, 2, FUN = mean), apply(port_3, 2, FUN = sd), weights)
port_3_plot = as.data.frame(port_3_plot)
port_3_plot$sharpe = port_3_plot$V1/port_3_plot$V2
port_3_plot$Label = "SPY_TMF"
colnames(port_3_plot) = c("E[R]", "Sigma", "W1", "W2", "Sharpe", "Asset Mix")

#SPXL_VGLT
SPXL_VGLT = cbind(annualReturn(SPXL), annualReturn(VGLT))
port_4 = SPXL_VGLT %*% t(weights)
port_4_plot = cbind(apply(port_4, 2, FUN = mean), apply(port_4, 2, FUN = sd), weights)
port_4_plot = as.data.frame(port_4_plot)
port_4_plot$sharpe = port_4_plot$V1/port_4_plot$V2
port_4_plot$Label = "SPXL_VGLT"
colnames(port_4_plot) = c("E[R]", "Sigma", "W1", "W2", "Sharpe", "Asset Mix")

EF = rbind(port_1_plot, port_2_plot, port_3_plot, port_4_plot)

EF_plot = ggplot(data = EF, aes(x = Sigma, y = `E[R]`, col = `Asset Mix`)) + geom_point()
EF_plot = EF_plot + ggtitle("Fig. 15: Last 3 Years Efficiency Frontiers") 
EF_plot + geom_abline(slope = max(EF$Sharpe))

kable(EF %>% group_by(`Asset Mix`) %>% filter(`Sharpe` == max(`Sharpe`))) 
```

