---
title: "An Analysis of Market ETFs"
author: "Art Tay"
date: "12/17/2020"
output: html_document
---

```{r, include=F}
# VTI = getSymbols(Symbols = "VTI", src = "yahoo", from = start, to = end, auto.assign = F)
# VTI = to.quarterly(VTI)
# #chartSeries(VTI)
# 
# VTI_Q = as.data.frame(quarterlyReturn(VTI))
# VTI_Q = VTI_Q %>% 
#   mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
#   mutate("Gross Returns" = quarterly.returns + 1) %>% 
#   mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
#   mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
#   mutate("Time" = index(VTI))
# 
# VTI_mean = mean(VTI_Q$`Quarterly Return Percent`)
# VTI_media = median(VTI_Q$`Quarterly Return Percent`)
# VTI_sd = sd(VTI_Q$`Quarterly Return Percent`)
# VTI_cum = last(VTI_Q$`Cum. Return Percent`)
# 
# VTI_plot_cum = ggplot(data = VTI_Q, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line()
# VTI_plot_cum + ggtitle("VTI Cummulative Returns") + ylab("Cummulative Percent Returns")
# 
# VTI_boxplot = ggplot(data = VTI_Q, aes(x = `Quarterly Return Percent`)) + geom_boxplot() 
# VTI_boxplot + ggtitle("VTI Quarterly Return BoxPlot")

```

```{r, include=F}
library(tidyverse)
library(quantmod)

start = "2015-1-1"
end = "2020-12-17"

```

# Equities

## US Indexes 
## Total Stock Market
```{r, echo=F}
name = "VTI"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```


## S&P 500 
```{r, echo=F}
name = "SPY"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```

## Dow Jones
```{r, echo=F}
name = "DIA"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```

## Nasdaq
```{r, echo=F}
name = "QQQ"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```


## Emerging Market Stocks
```{r, echo=F}
name = "VWO"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```

## International Market Stocks
```{r, echo=F}
name = "VXUS"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```

## European
```{r, echo=F}
name = "VGK"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```


## Asia
# Japan
```{r}
name = "JPXN"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```
# Chinese Tech 
```{r}
name = "CQQQ"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```


# Fix Income 
## US Gov
### Inflation Protected
```{r}
name = "VTIP"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```

### Long Term Treasuries
```{r}
name = "VUSTX"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```

## US Corporate
```{r}
name = "LQD"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```

## Real Estate
### REIT
```{r}
name = "VNQ"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```

### MBS
```{r}
name = "VMBS"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```

## Emerging Market Bonds
```{r}
name = "VWOB"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```

# Commodities
## Gold 
```{r}
name = "GLD"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```

## Agriculture
```{r}
name = "DBA"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```

## Energy 
```{r}
name = "DBE"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```

## Clean Energy
```{r}
name = "ICLN"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```

## Diversified
```{r}
name = "PDBC"

xts = to.quarterly(getSymbols(Symbols = name, src = "yahoo", from = start, to = end, auto.assign = F))

x = assign(paste(name, "_Q", sep = ""), as.data.frame(quarterlyReturn(xts)) %>% 
  mutate("Quarterly Return Percent" = quarterly.returns * 100) %>% 
  mutate("Gross Returns" = quarterly.returns + 1) %>% 
  mutate("Cum. Returns" = cumprod(`Gross Returns`)) %>% 
  mutate("Cum. Return Percent" = (`Cum. Returns`- 1) * 100) %>%  
  mutate("Time" = index(xts))) 

assign(paste(name, "median", sep="_"), median(x$`Quarterly Return Percent`))
assign(paste(name, "mean", sep="_"), mean(x$`Quarterly Return Percent`))
assign(paste(name, "sd", sep="_"), sd(x$`Quarterly Return Percent`))
assign(paste(name, "cum.", sep="_"), last(x$`Cum. Return Percent`))

ggplot(data = x, aes(x = Time, y = `Cum. Return Percent`)) + geom_point() + geom_line() + ggtitle(paste(name, "Cummulative Returns")) + ylab("Cummulative Percent Returns")

ggplot(data = x, aes(x = `Quarterly Return Percent`)) + geom_boxplot() + ggtitle(paste(name, "Quarterly Return BoxPlot"))
```

# Comparing Risk and Return
```{r, echo=F}

tickers = c("VTI", "SPY", "DIA", "QQQ", "VWO", "VXUS", "VGK", "JPXN", "CQQQ", "VTIP", "VUSTX", "LQD", "VNQ", "VMBS", 
            "VWOB", "GLD", "DBA", "DBE", "PDBC", "ICLN")

ret.df = cbind(VTI_Q$`Quarterly Return Percent`,SPY_Q$`Quarterly Return Percent`,DIA_Q$`Quarterly Return Percent`,
               QQQ_Q$`Quarterly Return Percent`, VWO_Q$`Quarterly Return Percent`, VXUS_Q$`Quarterly Return Percent`,
               VGK_Q$`Quarterly Return Percent`, JPXN_Q$`Quarterly Return Percent`, CQQQ_Q$`Quarterly Return Percent`,
               VTIP_Q$`Quarterly Return Percent`, VUSTX_Q$`Quarterly Return Percent`, LQD_Q$`Quarterly Return Percent`,
               VNQ_Q$`Quarterly Return Percent`, VMBS_Q$`Quarterly Return Percent`, VWOB_Q$`Quarterly Return Percent`,
               GLD_Q$`Quarterly Return Percent`, DBA_Q$`Quarterly Return Percent`, DBE_Q$`Quarterly Return Percent`, 
               PDBC_Q$`Quarterly Return Percent`, ICLN_Q$`Quarterly Return Percent`)

colnames(ret.df) = tickers

```

## Plots
```{r}
ret.df = as.data.frame(ret.df)
plotting = ret.df %>% gather(key = "Ticker", value = "Percent Returns")
plotting$Ticker=as.factor(plotting$Ticker)

ggplot(data = plotting, aes(x = Ticker, y = `Percent Returns`, col = Ticker)) + geom_violin() + 
  ggtitle("Quarterly Return Violin Plot")
ggplot(data = plotting, aes(x = Ticker, y = `Percent Returns`)) + geom_boxplot() + 
  ggtitle("Quarterly Return Boxplot")
```


## Corvariance Matrix
```{r}
library(corrplot)
(ret_cov = cov(ret.df))
(ret_cor = cor(ret.df))
(ret_corplot = corrplot(ret_cor, method = "ellipse"))
```

## Min-Var Portfolio
```{r}


#generate random portfolio weights 
rand_weight = data.frame()

for(i in 1:1000){
  r_vec = runif(20)
  norm = sum(r_vec)
  r_vec = r_vec / norm 
  rand_weight = rbind(rand_weight, r_vec)
}

```

```{r}
#create a cum. return vector 

#tickers = c("VTI", "SPY", "DIA", "QQQ", "VWO", "VXUS", "VGK", "JPXN", "CQQQ", "VTIP", "VUSTX", "LQD", "VNQ", "VMBS", 
#            "VWOB", "GLD", "DBA", "DBE", "PDBC", "ICLN")


cum_ret_vec = cbind(VTI_cum., SPY_cum., DIA_cum., QQQ_cum., VWO_cum., VXUS_cum., VGK_cum., JPXN_cum., 
                    CQQQ_cum., VTIP_cum., VUSTX_cum., LQD_cum., VNQ_cum., VMBS_cum., VWOB_cum., GLD_cum., 
                    DBA_cum., DBE_cum., PDBC_cum., ICLN_cum.)
```

```{r}

df = data.frame()

for(i in 1:nrow(rand_weight)){
  
  row = as.matrix(rand_weight[i,])
  ret = row %*% t(cum_ret_vec)
  var = row %*% ret_cov %*% t(row)
  row = append(row, ret)
  row = append(row, var)
  df = rbind(df, row)
  
}

```

```{r}

colnames(df) = c("VTI", "SPY", "DIA", "QQQ", "VWO", "VXUS", "VGK", "JPXN", "CQQQ", "VTIP", "VUSTX", "LQD", "VNQ", "VMBS",
                 "VWOB", "GLD", "DBA", "DBE", "PDBC", "ICLN", "R_p", "Var_p")

df$SD = sqrt(df$Var_p)

df$Sharpe = df$R_p / df$SD

df[which.max(df$Sharpe),]

ggplot(data = df, aes(x = SD, y = R_p)) + geom_point() 

```

# Portfolio Testing 
```{r}
port_tickers = c("VUSTX", "VMBS", "SPY", "EMB", "CQQQ", "ICLN")


port_weights = c(.4, .1, .2, .1, .1, .1)  

port_ret = data.frame()
for(i in port_tickers){
  rs = getSymbols(Symbols = i, src = "yahoo", auto.assign = F, from = start, to = end)
  rs = weeklyReturn(rs)
  port_ret = cbind(port_ret, rs)
}

colnames(port_ret) = port_tickers

rets = t(port_weights) %*% t(port_ret)

rets = t(rets)

rets = as.data.frame(rets)

rets$Gross = rets$V1 + 1

port_cum = cumprod(rets$Gross)-1
  
port_sd = sd(rets$V1)

port_sharpe = last(port_cum)/port_sd

last(port_cum)

```


# Takeaways 
1. Most market indexes return about 5-7% quarter with differing levels of volatility. 
2. The most inversely correlated securities to the general market are Mortgage-Backed Securities and Long-Term U.S. treasures. 
3. MBS return are historically so close to zero they are not a wrote wild investment. 
4. Most markets move together even when factoring sector overweighting and geography. 

# Next Steps
It seems that the majority of the benefits of diversifiaction can be reaped by just investing in the S&P 500 and Long-Term U.S. treasures. Given the stability of this portfolio employing leverage should yield asymmetric upside. 
